---
title: "My Shiny App Documentation"
author: "ENA"
date: "December 22, 2017"
runtime: shiny
output: html_document
---

The purpose of this application is to explore the realtion between miles per gallon and transmission type, number of cylinders, and gears.

For this purpose we created a shiny application that has one independent variable, observed characteristic, and one dependent variable, MPG.  The standard mtcars dataset propived with R is used for this application.

Our goal is to answer the follwoing questions

1. Does MPG increase or decrease as the number of cylinders grow
2. Does MPG increase or decrease as the number of gears increase
3. Do the automatic or manual cars have higher MPG

Our shiny application has a side bar panel and and a main panel. In the side bar panel there is one drop down list box with 3 choices - cylinders, gears, transmission. Based on the choice of that input, there is a MPG graphic displayed in the main panel.

Here is how the input looks like.  You can change the observed characteristic and find out how the output looks like.

```{r echo = FALSE}
library(shiny)
library(datasets)

selectInput("variable", "Observed Characteristic:",
                    list("Cylinders" = "cyl", 
                         "Gears" = "gear",
                         "Transmission" = "am"))
```


Here is the output. You can easily answer the questions above by changing the input and observe the output.

```{r echo = FALSE}
renderPlot({
    mpgData <- mtcars
    mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
        
    # Compute the forumla text in a reactive expression
    formulaText <- reactive({
        paste("mpg ~", input$variable)
    })
    
    # Return the formula text for printing as a title
    output$title <- renderText({
        formulaText()
    })
    
        plot(formula = as.formula(formulaText()), 
             data = mpgData,
             xlab = input$variable,
             ylab = "mpg",
             type="o",
             col = "dark green")
    })

```